---
title: "Storm data analysis"
author: "Shin-Fu Chen"
date: "2019/9/22"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Storm data analysis

This is an analysis report of storm data.
There are two questions we want to analyze, they are:

1. Across the United States, which types of events are most harmful with respect to population health?

2. Across the United States, which types of events have the greatest economic consequences?

***
In this report, there are three parts of chapter, first is Data Processing, second is Results, and third is summary.
***

## Data Processing

Firstly, we read data from raw data, and check the data structure.
```{r}
rawStorm <- read.csv("repdata_data_StormData.csv.bz2",encoding = "UTF-8")
str(rawStorm )
```
Because we want to analyze about costes of  population health and economic consequence, so we only keep the variables we need to use.
Also, we have to change the class of data from factor into numeric class.

```{r}
data<-rawStorm [,c("EVTYPE","FATALITIES",
                   "INJURIES", "PROPDMG",
                  "CROPDMG")]
data[,c(2:5)]<-sapply(data[,c(2:5)],as.character) %>% sapply(as.numeric)


```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
